Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-02 thesis/thesis.tex
thesis: Move list of figures and tables
Co-Authored-By: Cesar Guzmann <15159632+cguz@users.noreply.github.com>
thesis: Add some corrections

The characterization and knowledge of \emph{Open Clusters} allow us to better understand properties and mechanisms about the Universe
such as stellar formation and the regions where those events occur.
They also provide information about stellar processes and the evolution of the galactic disk.

@@

\chapter{Acknowledgement}

@@

Stellar open clusters (OCs) \cite{janes1982open} are groups of stars gravitationally bound originated from a single molecular gas cloud.
They share the same chemical composition and age. Moreover, they have similar relative positions and proper motion.
Those astronomical objects are relevant to understand the spiral structure, the dynamics and the chemical evolution of our galaxy.

Although most stars in the Milky Way are presented isolated, it is considered that most of them (or even all)
are formed in clustered environments and spend a period of time gravitationally bound with their siblings embedded
in their original molecular cloud \cite{clarke2000theformationofstellarclusters} \cite{portegies2010young}.
The evolution of those systems tends to sparse them in a few million years by interacting gravitationally with other systems.
Galactic tidal forces and mechanisms that involves gas loss driven by stellar feedback are other causes of disruption
\cite{brinkmann2017bound}.
Nevertheless, a small fraction of those systems will survive in the initial state and persist bound in bigger timescales.

Young OCs allow us to research stars formation regions and improve our understanding about the mechanisms that create those stars.
On the other hand, older open clusters give us information about stellar processes and how the galactic disk evolves.
Some highly disturbed orbits could also provide evidence of recent merge events and accretion traces from outside the galaxy
\cite{cantat2016abundances}.

@@

Although the members of a cluster appear in the observation visual field as an overdensity in positions,
as shown in Figure \ref{fig:pos_ngc_2682},
these coordinates are not useful to separate those stars that belong to the cluster from the other which do not.
However, if we look for overdensities in the proper motions configuration space, it is possible, at least at first instance,
to assume a possible membership delimitation (see Figure \ref{fig:pm_ngc_2682}.

@@

To achieve the general goal, we will follow the following milestones:

@@

An initial approach for finding OCs is the search of overdensities along the galactic disk. In general, this is the starting point but,
although it seems simple, it presents a fundamental problem already discussed. The near field around the OC is filled with two types of
distinct stars populations: those who belong to the OC (tens or hundreds to a few thousand) and a background made up of thousands or
millions of stars that are not. Finding out which stars belong to the first group is the problem treated in this work.
This selection is crucial to properly characterize the fundamental properties of the cluster
(dynamics, total mass, age, chemical composition, etc.).

@@

At this point, it seems reasonable that the study of each individual group requires its own parametrization and technique
to identify it. With Gaia DR2, which contains great high-quality astrometric and photometric data for a huge number of stars,
a new opportunity presents itself to simplify and optimize these processes. In this context, new approaches are being developed
to improve current detection methods and automate OC characterization.

@@

In this context, and taking advantage of the opportunity provided by Gaia DR2, new approaches are being developed to improve current
detection methods and automating OC characterization as much as possible. This is the case of tools such as Clusterix 2.0
\cite{balaguer2020clusterix}, TOPCAT \cite{taylor2005topcat}, and VOSA \cite{bayo2008vosa}, (all of them developed by the Virtual Observatory).
These tools work together and offer good results, although it is not possible to use them in an unattended process and free of certain
different parametrization in each case.

@@

TOPCAT alone does not offer an independent discrimination mechanisms to researchers. They should try an initial selection, staring from the
map of proper motions, by delimiting the area where the cluster presumably appears. When this is not possible, it is necessary to have a
certain knowledge about the cluster profile and to parametrize some approximated values. In both cases, the definition of the selected
set must then be optimized step by step until reaching a result that can be considered reasonable.

Another tool is Clusterix 2.0, which is an interactive web-based tool \cite{balaguer2020clusterix}. It takes the proper motion diagram
without assuming any prior profiles assumptions for the stars candidates membership and determines empirically the frequency functions.

@@

\begin{displayquote}
The non-field population does not occupy the entire workspace, but is spatially concentrated, which makes it possible to distinguish two regions
in the workspace: the only field region (label 'f'), dominated by stars field, and the cluster + field region (label 'c+f'), which includes field
stars and not field stars. \cite{balaguer2020clusterix}
\end{displayquote}

This fact implies defining three areas or regions with different radius. The first 'c+f' corresponds to the one in which the cluster members are
presumed to be contained together with other field stars that are not part of the cluster. The second, broader, assumes that it only contains
stars in an extended visual field without components of the cluster, and a third intermediate region, which is out of analysis (void area), which
would correspond to a possible transition zone between the other two.

@@

It should be noted that for the execution of this method, MareNostrum 42 (Bacelona Supercomputing Center) was used. So the neural network could handle
the image recognition process with isochrone patterns and not applying theoretical models derived from values such as metallicity, masses, among other.

@@

Our aim in this work, linked to computational limitations compared to MareNostrum, is not to do a blind search for clusters, but to obtain a method,
in the machine learning environment, that allows the characterization of open clusters through unsupervised and non-parametrized procedures in a
single step. This method should not require further refinements with other tools.

@@

For the sake of simplicity, we are taking \emph{Melotte 22 (Messier 45)} \cite{elsanhoury2019ppmxl} to illustrate the whole method. This cluster is well studied
and their stars are not too mixed with other region stars, so images look clearly.

@@

This download is not limited to the size registered in the catalogue.
Instead, a wider region (1.5 times the size of the cluster) is downloaded for each cluster to include stars outside the cluster.
The idea is that the unsupervised model must be able to clusterize the stars that belongs to the OC and to discard
those outsiders when characterizing the open cluster.

@@

Taking these considerations into account, the downloaded dataset covers nearly 114 million stars (42GB of compressed data). This dataset is significantly
smaller than the whole Gaia DR2 dataset, which contains information for approximately 1,600 million stars. However, it is still being too large.

@@

So, a cluster must fulfil the following filters to be accepted:

@@

As shown in Figure \ref{fig:OpenClustSelection}, these constrains give us a smaller dataset but it is still being a good representation of all clusters in the Milky Way
since they are equally distributed around the galaxy disk.

@@

PostgreSQL knows that all stars we want to are located inside \verb|gaiadr2.region_302| so it does not need to query any other tables.
This allows us to download data for as many regions as we want to without loosing efficiency when accessing for that data.

@@

The downloader takes data from the Gaia DR2 database and save the selection into our custom database without modifying any value,
so data preserves all its properties and units.

Python methods for retrieving information from the database are available through an instance of \verb|cdalvaro.DB|.
This class contains methods for recovering stars information for a given region as a Pandas \verb|DataFrame| ready for data analysis.

@@

As mentioned before, we want our model to characterize open clusters by looking at their dynamics properties.

Also, we want to maintain as simple as possible our clustering model in order to avoid requiring too much computing resources.

@@

However, we are not going to use these raw features. Instead, we are taken a combination of them.

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/melotte_22/features_melotte_22.png}
  \end{subfigure}
  \caption{Melotte 22 feature pairplot}
  \label{fig:features_melotte_22}
\end{figure}

@@

To solve this issue, we will try to estimate the best number of clusters by using one more time the \emph{silhouette score}.

@@

K-Means does a good job making an initial clustering, as shown in Figure \ref{fig:kmeans_melotte_22}. However, too many clusters arise from this characterization
and the open cluster is still polluted with stars that do not belong to it. Even more, we would like to reduce the amount of clusters too.

@@

If we take a look into the H-R diagram (Figure \ref{fig:kmeans_hr_diagram_melotte_22}), we can identify the isochrone curve for Melotte 22 cluster.
This curve has a good shape, but again, it contains outsider stars. Therefore, we would like to find a better model that improves this initial characterization
by reducing the amount of clusters and also that would be able to remove outsiders from the OC.

@@

Our initial approach allows us to find some groups that potentially contain the desired OC. However, as we have seen, the result is not enough
accurate. Therefore, we need a method for merging clusters by migrating stars from one group to another,
so we can end up with the minimum number of clusters while preserving the open cluster.

Since we do not have a labeled dataset which allows us to train a supervised model, we have no choice but to use an unsupervised self-trained model.

@@

Although, as explained in section \ref{sec:feature_selection}, the number of features we are managing is not too large, this latent space allows us to reduce
the number of features, avoiding this way the \emph{"curse of dimensionality"} \cite{bellman1961curse}.

These encoders are pretrained before fitting the model to generate predictions. Then, the encoder is used to transform input data to the
latent space $Z$. Once the data has been transformed, a K-Means clusterer is used to make an initial clustering.

@@

Figure \ref{fig:dec_model_setup} shows the layer setup of our DEC model. It is simpler than the one tested on the original paper \cite{xie2016unsupervised},
since the number of selected features in our work is smaller. Therefore, using the same configuration would result in a model too
powerful that would incur in overfitting issues unable to make right predictions.

@@

As shown in Figure \ref{fig:dec_melotte_22}, the DEC model is able to move stars from one group to another removing some clusters and improving the OC characterization.
This is exactly what we are looking for.

@@

For that reason, we have used an alternative method based on Virtual Observatory (VO) tools such as Clusterix and TOPCAT,
to characterize the studied clusters.

@@

The aim of this section is to highlight procedure differences between the our method and this new one,
as well as using the results given by this method to validate ours results.
This validation method uses a combination of VO tools: Clusterix 2.0 + TOPCAT.
We take Melotte 22 again as our study case to make easier taking comparisons between the method presented in Chapter \ref{chap:method}
and this alternative method.

The initial point, in order to avoid a subjective and manual selection for the cluster members, is taking advantage of Clusterix.
Figure \ref{fig:clusterix_selection} shows a screenshot of the Clusterix 2.0 selection panel.

@@

This panel allows us to select a region by its coordinates or by searching a cluster by its name in the Gaia DR2 catalogue,
and specify the size of the region by introducing its radius.
We can also set limit values in magnitude (for both, minimum and maximum) to discard stars outside those limits.
Another setting is the flag to enable or disable the \emph{Q-Filter}.
This filter discards those stars with \emph{null} values in relevant fields.

@@

It is necessary to notice the importance of this step, since the selection of these regions is critical to get a good result.
However, despite how crucial is this selection, there is no general rule to define these regions.
We only have two references: the radius of the downloaded region and the estimated size for the open cluster that sets the \emph{inner radius}.
The other two radius must be set by trial and error and, in general, they must be generous to be sure we are not taking polluted regions.
This is a tedious process that requires several tries before achieving good enough probability values.

Furthermore, it is necessary to know in advance some additional profile of the cluster, in addition to the estimated size.
For example, in the case of Melotte 22, the proper motion in declination direction of the membership stars is around $-45 mas \cdot year^{-1}$,
so it is necessary to open the $\mu$ range above the estimated values (in absolute value). If we do not do that we loose its detection,
since Clusterix sets this value to $30 mas \cdot year^{-1}$ by default. But even in this case, it is necessary to set a threshold for
magnitude values, $G \leq 14$, to help getting the right result.
Figure \ref{fig:clusterix_step2_melotte_22} shows the region selection panel on Clusterix 2.0.

@@

This step can be repeated over and over again, varying radii and other parameters, until finally reach a valid probability that works.
The last step presents a table with candidates objects and allows to export this dataset to TOPCAT,
Aladin and VOSA to perform a deeper filtering and analysis based on the results given by Clusterix.

@@

Once data is available in TOPCAT, we have to carefully analyze the imported data.
From there, we can perform a first stars selection by excluding those stars with probability value lower than 0.8.
This first result can be taken as a good staring point, but we still need to make some fine tunning.
As we can see in Figure \ref{fig:topcat_prob_selection_melotte_22}, the selection is too restrictive and we have lost too many stars.

@@

Taken these observations into account, we can proceed to make a new selection based on parallax properties.
Our second selection uses the values obtained with the previous selection for parallax and its standard deviation and
selects those stars from the whole set which fall inside the limits $7.304mas \pm 0.797$ (see Figure \ref{fig:topcat_parallax_melotte_22}).

@@

Until now, we have focused our study in the open cluster Melotte 22.
Since our aim is to get a model that fits well for a wide range of clusters,
we present now some results obtained for a selection of clusters with different topologies.

All results have been computed with an Apple Mac Pro Late 2013, 2.7 GHz 12-Core Intel Xeon E5 with two AMD FirePro D700 6GB and 64 GB
of memory, running macOS BigSur 11.0.1, Keras 2.2 and PlaidML 0.7.

>>>>

The characterization and knowledge of \emph{Open Clusters} allow us to better understand properties and mechanisms about the Universe
such as stellar formation and the regions where these events occur.
They also provide information about stellar processes and the evolution of the galactic disk.

@@

\chapter{Acknowledgements}

@@

Stellar open clusters (OCs) \cite{janes1982open} are groups of stars gravitationally bounded originated from a single molecular gas cloud.
They share the same chemical composition and age. Moreover, they have similar relative positions and proper motion.
Those astronomical objects are relevant to understand the spiral structure, the dynamics and the chemical evolution of our galaxy.

Although most stars in the Milky Way are presented isolated, it is considered that most of them (or even all)
are formed in clustered environments and spend a period of time gravitationally bounded with their siblings embedded
in their original molecular cloud \cite{clarke2000theformationofstellarclusters} \cite{portegies2010young}.
The evolution of those systems tends to sparse them in a few million years by interacting gravitationally with other systems.
Galactic tidal forces and mechanisms that involve gas loss driven by stellar feedback are other causes of disruption
\cite{brinkmann2017bound}.
Nevertheless, a small fraction of those systems will survive in the initial state and persist bounded in bigger timescales.

Young OCs allow us to research star formation regions and improve our understanding about the mechanisms that create those stars.
On the other hand, older open clusters give us information about stellar processes and how the galactic disk evolves.
Some highly disturbed orbits could also provide evidence of recent merge events and accretion traces from outside the galaxy
\cite{cantat2016abundances}.

@@

Although the members of a cluster appear in the observational visual field as an overdensity in positions,
as shown in Figure \ref{fig:pos_ngc_2682},
these coordinates are not useful to separate those stars that belong to the cluster from the other that do not.
However, if we look for overdensities in the proper motion configuration spaces, it is possible, at least at first instance,
to assume a possible membership delimitation (see Figure \ref{fig:pm_ngc_2682}.

@@

To achieve the general goal, we will set the following milestones:

@@

An initial approach for finding OCs is the search of overdensities along the galactic disk. In general, this is the starting point but,
although it seems simple, it presents a fundamental problem already discussed. The near field around the OC is filled with two types of
distinct star populations: those who belong to the OC (tens or hundreds to a few thousand) and a background made up of thousands or
millions of stars that are not. Finding out which stars belong to the first group is the problem faced in this work.
This selection is crucial to properly characterize the fundamental properties of the cluster
(dynamics, total mass, age, chemical composition, etc.).

@@

At this point, it seems reasonable that the study of each individual group requires its own parametrization and technique
to identify it. With Gaia DR2, which contains great high-quality astrometric and photometric data for a huge number of stars,
a new opportunity arises to simplify and optimize these processes. In this context, new approaches are being developed
to improve current detection methods and automate OC characterization.

@@

In this context, and taking advantage of the opportunity provided by Gaia DR2, new approaches are being developed to improve current
detection methods and automating OC characterization as much as possible. This is the case of tools such as Clusterix 2.0
\cite{balaguer2020clusterix}, TOPCAT \cite{taylor2005topcat}, and VOSA \cite{bayo2008vosa}, (all of them developed by the Virtual Observatory).
These tools work together and offer good results, although it is not possible to use them in an unsupervised process and free of certain
different parametrization in each case.

@@

TOPCAT alone does not offer an independent discrimination mechanisms to researchers.
They should try an initial selection, starting from the map of proper motions,
by delimiting the area where the cluster presumably appears. When this is not possible, it is necessary to have a
certain knowledge about the cluster profile and to parametrize some approximated values.
In both cases, the definition of the selected set must then be optimized step by step until reaching a result that can be considered reasonable.

Another tool is Clusterix 2.0, which is an interactive web-based tool \cite{balaguer2020clusterix}.
It takes the proper motion diagram without making any prior assumptions about the membership of the candidate star
and determines empirically the frequency functions.

@@

\begin{displayquote}
The non-field population does not occupy the entire workspace, but is spatially concentrated, which makes it possible to distinguish two regions
in the workspace: the only field region (label 'f'), dominated by star fields, and the cluster + field region (label 'c+f'),
which includes both star fields and not star fields. \cite{balaguer2020clusterix}
\end{displayquote}

This fact implies defining three areas or regions with different radius. The first 'c+f' corresponds to the one in which the cluster members are
presumed to be contained together with other star fields that are not part of the cluster. The second, broader, assumes that it only contains
stars in an extended visual field without components of the cluster, and a third intermediate region, which is out of analysis (void area), which
would correspond to a possible transition zone between the other two.

@@

It should be noted that for the execution of this method, MareNostrum 42 (Barcelona Supercomputing Center) was used.
So the neural network could handle the image recognition process with isochrone patterns and not applying theoretical models
derived from values such as metallicity, masses, among other.

@@

Our aim in this work, linked to computational limitations compared to MareNostrum, is not to do a blind search for clusters,
but to obtain a method, within the machine learning environment,
that allows the characterization of open clusters through unsupervised and non-parametrized procedures in a single step.
This method should not require further refinements with other tools.

@@

For the sake of simplicity, we are taking \emph{Melotte 22 (Messier 45)} \cite{elsanhoury2019ppmxl} to illustrate the whole method.
This cluster is well studied and its stars are not too mixed with other stars that do not belong to the OC although they are contained
in the same observation field, so images look clear.

@@

This download is not limited to the size registered in the catalogue.
Instead, a wider region (1.5 times the size of the cluster) is downloaded for each cluster to include stars outside the cluster.
The idea is that the unsupervised model must be able to clusterize the stars that belong to the OC and to discard
those outsiders when characterizing the open cluster.

@@

Taking these considerations into account, the downloaded dataset covers nearly 114 million stars (42GB of compressed data).
This dataset is significantly smaller than the whole Gaia DR2 dataset, which contains information for approximately 1,600 million stars.
However, it is still too large.

@@

Therefore, a cluster must fulfil the following filters in order to be accepted:

@@

As shown in Figure \ref{fig:OpenClustSelection}, these constrains give us a smaller dataset but it is still a good representation of all clusters in the Milky Way
since they are equally distributed around the galaxy disk.

@@

PostgreSQL knows that all stars we want are located inside \verb|gaiadr2.region_302| so it does not need to query any other table.
This allows us to download data for as many regions as we want without loosing efficiency when accessing for that data.

@@

The downloader takes data from the Gaia DR2 database and saves the selection into our custom database without modifying any value,
so data preserves all its properties and units.

Python methods for retrieving information from the database are available through an instance of \verb|cdalvaro.DB|.
This class contains methods for retrieving star's information for a given region as a Pandas \verb|DataFrame|, ready for data analysis.

@@

As mentioned before, we want our model to characterize open clusters by looking at their dynamic properties.

Also, we want to maintain as simple as possible our clustering model in order to save computing resources.

@@

However, we are not going to use these raw features. Instead, we are taking a combination of them.

@@

\begin{figure}[htbp]
  \centering
  \begin{subfigure}{\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/melotte_22/features_melotte_22.png}
  \end{subfigure}
  \caption{Melotte 22 feature pairplot}
  % TODO: Ampliar la descripción de la figura
  \label{fig:features_melotte_22}
\end{figure}

@@

To solve this issue, we will try to estimate the best number of clusters by using the \emph{silhouette score} one more time.

@@

K-Means does a good job making an initial clustering, as shown in Figure \ref{fig:kmeans_melotte_22}.
However, too many clusters arise from this characterization and the open cluster is still polluted with stars that do not belong to it.
Moreover, we would like to reduce the amount of clusters too.

@@

If we take a look into the H-R diagram (Figure \ref{fig:kmeans_hr_diagram_melotte_22}),
we can identify the isochrone curve for Melotte 22 cluster.
This curve has a good shape, but again, it contains outsider stars.
Therefore, we would like to find a better model that improves this initial characterization
by reducing the amount of clusters and also that removes outsiders from the OC.

@@

Our initial approach allows us to find some groups that potentially contain the desired OC.
However, as we have seen before, the result is not enough accurate.
Therefore, we need a method for merging clusters by migrating stars from one group to another,
so we can end up with the minimum number of clusters while preserving the open cluster.

Since we do not have a labeled dataset to train a supervised model,
we have no choice but to use an unsupervised self-trained model.

@@

Although, as explained in section \ref{sec:feature_selection}, the number of features we are managing is not too large,
this latent space helps us reduce the number of features and avoids the \emph{"curse of dimensionality"} \cite{bellman1961curse}.

These encoders are pretrained before fitting the model to generate predictions.
Then, the encoder is used with he aim of transforming input data to the latent space $Z$.
Once the data has been transformed, a K-Means clusterer is used in order to make an initial clustering.

@@

Figure \ref{fig:dec_model_setup} shows the layer setup of our DEC model.
It is simpler than the one tested on the original paper \cite{xie2016unsupervised},
since the number of selected features in our work is smaller.
Therefore, using the same configuration would result in a model so
powerful that would incur in overfitting issues unable to make right predictions.

@@

As shown in Figure \ref{fig:dec_melotte_22}, the DEC model is able to move stars from one group to another,
removing some clusters and improving the OC characterization.
This is exactly what we are looking for.

@@

For that purpose, we have used an alternative method based on Virtual Observatory (VO) tools such as Clusterix and TOPCAT,
to characterize the studied clusters.

@@

The aim of this section is to highlight the procedure differences between our method and this new one,
as well as using the results provided by this method to validate ours results.
This validation method uses a combination of VO tools: Clusterix 2.0 + TOPCAT.
We take Melotte 22 again as our study case to make easier comparisons between the method presented in Chapter \ref{chap:method}
and this alternative one.

The initial point is taking advantage of Clusterix in order to avoid a subjective and manual selection for the cluster members.
Figure \ref{fig:clusterix_selection} shows a screenshot of the Clusterix 2.0 selection panel.

@@

This panel allows us to select a region by its coordinates or by searching a cluster by its name in the Gaia DR2 catalogue,
as well as specify the size of the region by introducing its radius.
We can also set limit values in magnitude (for both minimum and maximum) to discard stars outside these limits.
Another setting is the flag to enable or disable the \emph{Q-Filter}.
This filter discards those stars with \emph{null} values in relevant fields.

@@

It is necessary to remark the importance of this step, since the selection of these regions is critical to get a good result.
However, despite how crucial is this selection, there is no general rule to define these regions.
We only have two references: the radius of the downloaded region and the estimated size for the open cluster that sets the \emph{inner radius}.
The other two radius must be set by trial and error. In general, they should be large enough to be sure we are not taking polluted regions.
This is a tedious process that requires several tries before achieving good enough probability values.

Furthermore, it is necessary to know in advance some additional profiles of the cluster, in addition to the estimated size.
For example, in the case of Melotte 22, the proper motion in declination direction of the membership stars around $-45 mas \cdot year^{-1}$,
so it is necessary to open the $\mu$ range above the estimated values (in absolute value).
If we do not do that we lose the possibility of detection, since Clusterix sets this value to $30 mas \cdot year^{-1}$ by default.
But even in this case, it is necessary to set a threshold for magnitude values, $G \leq 14$, to help getting the right result.
Figure \ref{fig:clusterix_step2_melotte_22} shows the region selection panel on Clusterix 2.0.

@@

This step can be repeated over and over again, varying radii and other parameters, until finally reach a valid probability that works.
The last step presents a table with candidate objects and allows to export this dataset to TOPCAT,
Aladin and VOSA to perform a deeper filtering and analysis based on the results provided by Clusterix.

@@

Once data is available in TOPCAT, we have to carefully analyze the imported data.
From there, we can perform a first star selection by excluding those stars with probability value lower than 0.8.
This first result can be taken as a good starting point, but we still need to make some fine tunning.
As we can see in Figure \ref{fig:topcat_prob_selection_melotte_22}, the selection is too restrictive and we have lost too many stars.

@@

Taken these observations into account, we can proceed to make a new selection based on parallax properties.
Our second selection makes use of the values obtained with the previous selection for parallax and its standard deviation and
selects those stars from the whole set which fall inside the limits $7.304mas \pm 0.797$ (see Figure \ref{fig:topcat_parallax_melotte_22}).

@@

Until now, we have focused our study in the open cluster Melotte 22.
Since our aim is to get a model that fits well for a wide range of clusters,
we will now proceed to show some results obtained for a selection of clusters with different topologies.

All results have been computed with an Apple Mac Pro Late 2013, 2.7 GHz 12-Core Intel Xeon E5 with two AMD FirePro D700 6GB and 64 GB
of memory, running macOS BigSur 11.1, Keras 2.2 and PlaidML 0.7.
